### 2009-06-12 paper.tex
Minor changes.

The results of our simulations, illustrated in \figref{simulations},
demonstrate that the accuracy of both structural
reconstruction and alignment accuracy depend on the outgroup
branch length.  However, while the difficulty of alignment inference
increases in proportion to the outgroup branch length, becoming
near-impossible for very long outgroup branch lengths, the same need
not be true for structural reconstruction accuracy.  As the branch
length of the outgroup increases, the outgroup's structure becomes increasingly decoupled from
that of its ancestor, allowing the scoring scheme to ``ignore'' the
information which it contains.
In the trivial case where the outgroup branch length is zero (so the ancestor is identical to the outgroup),
we can perfectly reconstruct the ancestral structure (as expected),
but we cannot perfectly reconstruct the three-way multiple alignment
 (since there are still two finite-length branches,
 which on average contribute a greater-than-zero rate of unreconstructable mutations).

@@

To compare \indiegram\ to simpler reconstruction methods, we also measured the alignment accuracy using various simpler statistical reconstruction techniques.
We evaluated three maximum likelihood inference algorithms that use simpler gap-aware phylogenetic models,
and one posterior decoding algorithm that uses a non-phylogenetic sum-of-pairs scoring scheme.
These results are plotted on \figref{simulations} alongside the \indiegram\ accuracies.
In detail, the reconstruction methods used were

>>>>

The results of our simulations, illustrated in \figref{simulations},
demonstrate that while the difficulty of alignment inference increases
in proportion to the outgroup branch length, becoming very challenging
for long outgroup branch lengths, the same need not be true for
structural reconstruction accuracy.  As the branch length of the
outgroup increases, the outgroup's structure becomes increasingly
decoupled from that of its ancestor, allowing the scoring scheme to
``ignore'' the information which it contains.  In the trivial case
where the outgroup branch length is zero (so the ancestor is identical
to the outgroup), we can perfectly reconstruct the ancestral structure
(as expected), but we cannot perfectly reconstruct the three-way
multiple alignment (since there are still two finite-length branches,
which on average contribute a greater-than-zero rate of
unreconstructable mutations).

@@

To compare \indiegram\ to simpler reconstruction methods, we also measured the alignment accuracy using various simpler statistical reconstruction techniques.
We evaluated three maximum likelihood inference algorithms that use simpler gap-aware phylogenetic models
and one posterior decoding algorithm that uses a non-phylogenetic sum-of-pairs scoring scheme.
These results are plotted on \figref{simulations} alongside the \indiegram\ accuracies.
In detail, the reconstruction methods used were
